---
title: "NHP Outputs Report (Extract B)"
output:
  html_document:
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
params:
  r: NA
  sites: NA
  wd: ".."
---

```{r}
#| label: setup
#| echo: false

knitr::opts_chunk$set(error = TRUE, echo = FALSE, out.width = "100%")
pkgload::load_all(params$wd, quiet = TRUE)
```

```{r}
#| label: site-selections
#| echo: false

sites_were_selected <- if (is.null(params$sites)) FALSE else TRUE

if (sites_were_selected) {
  site_status <- "selected sites"

  site_lookup <- yyjsonr::read_json_file(app_sys("app", "data", "sites.json"))
  sites_list <- site_lookup[params$sites]

  selected_sites <-
    paste0(sites_list, " (", names(sites_list), ")") |>
    sort() |>
    stringr::str_flatten(collapse = ", ", last = " and ")
} else {
  site_status <- selected_sites <- "all sites"
}
```

---
subtitle: "Scenario: `r params$r$params$scenario` (`r site_status`)"
---

# Notes

This report provides the outputs (tables and charts) from the selected model
scenario (`r params$r$params$scenario`) for the following sites combined:
`r selected_sites`.

Note that some tables and charts won't be generated if there was insufficient
data to produce them, given the combination of trust and site selections
(if any).

This document is produced dynamically and so plots may not be produced at
optimal size.
Please [contact The Strategy Unit Data Science team][suds_email] if this is a
problem.

[suds_email]: mailto:mlcsu.su.datascience@nhs.net

See [the project information site][proj_info] for an overview of the model and
its methodology.

[proj_info]: https://connect.strategyunitwm.nhs.uk/nhp/project_information

# Metadata

This table shows the metadata for the selected model run:

```{r}
#| label: params-model-run

p <- get_params(params$r)
tabulate_model_run_info(p)
```

```{r}
#| label: isolate-results
results <- params$r$results
```

# Principal projection

## Summary

Bed-availability data is not available at site level.
See [the model project information site][proj_gloss] for definitions of terms.

[proj_gloss]: https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html

```{r}
#| label: pp-summary

results |>
  reskit::compile_principal_pod_data(
    get_condensed_pod_lookup(),
    params$sites
  ) |>
  reskit::make_principal_pod_table() |>
  gt::tab_options(table.align = "left")
```

## Length of stay summary

### Bed days

```{r}
#| label: pp-summary-los-beddays

results |>
  reskit::compile_principal_los_data(
    measure = "beddays",
    pod_lookup = get_pod_lookup(),
    sites = params$sites
  ) |>
  reskit::make_principal_los_table() |>
  gt::tab_options(table.align = "left")
```

### Admissions

```{r}
#| label: pp-summary-los-admissions

results |>
  reskit::compile_principal_los_data(
    measure = "admissions",
    pod_lookup = get_pod_lookup(),
    sites = params$sites
  ) |>
  reskit::make_principal_los_table() |>
  gt::tab_options(table.align = "left")
```

## Impact of changes

The results should be regarded as rough, high-level estimates of the number of
rows added/removed due to each parameter.
The plots here show results for all points of delivery combined.
See [the model project information site][proj_gloss] for definitions of terms.

```{r}
#| label: pp-impact-of-changes-setup

# Stopgap values so the ICF chart content is visible, see:
# https://github.com/The-Strategy-Unit/nhp_outputs/issues/427
icf_fig_height <- 7
icf_font_size <- 10
```

### Inpatients

#### Bed days

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-ip-bed-days

results |>
  reskit::compile_grouped_impact_data(
    measure = "beddays",
    activity_type = "ip",
    sites = params$sites,
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup()
  ) |>
  reskit::make_grouped_impact_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-ip-bed-days

results |>
  reskit::compile_tpma_impact_data(
    measure = "beddays",
    activity_type = "ip",
    sites = params$sites,
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup(),
    sort_by = "value"
  ) |>
  reskit::make_tpma_impact_plot()
```

#### Admissions

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-ip-admissions

results |>
  reskit::compile_grouped_impact_data(
    measure = "admissions",
    activity_type = "ip",
    sites = params$sites,
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup()
  ) |>
  reskit::make_grouped_impact_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-ip-admissions

results |>
  reskit::compile_tpma_impact_data(
    measure = "admissions",
    activity_type = "ip",
    sites = params$sites,
    sort_by = "value",
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup()
  ) |>
  reskit::make_tpma_impact_plot()
```

### Outpatients

#### Attendances

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-op-attendances

results |>
  reskit::compile_grouped_impact_data(
    measure = "attendances",
    activity_type = "op",
    sites = params$sites,
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup()
  ) |>
  reskit::make_grouped_impact_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-op-attendances

results |>
  reskit::compile_tpma_impact_data(
    measure = "attendances",
    activity_type = "op",
    sites = params$sites,
    sort_by = "value",
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup()
  ) |>
  reskit::make_tpma_impact_plot()
```

#### Tele-attendances

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-op-tele-attendances

results |>
  reskit::compile_grouped_impact_data(
    measure = "tele_attendances",
    activity_type = "op",
    sites = params$sites,
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup()
  ) |>
  reskit::make_grouped_impact_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-op-tele-attendances

results |>
  reskit::compile_tpma_impact_data(
    measure = "tele_attendances",
    activity_type = "op",
    sites = params$sites,
    sort_by = "value",
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup()
  ) |>
  reskit::make_tpma_impact_plot()
```

### A&E

#### Arrivals

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-aae-arrivals

results |>
  reskit::compile_grouped_impact_data(
    measure = "arrivals",
    activity_type = "aae",
    sites = params$sites,
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = get_pod_lookup()
  ) |>
  reskit::make_grouped_impact_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-aae-arrivals

results |>
  reskit::compile_tpma_impact_data(
    measure = "arrivals",
    activity_type = "aae",
    sites = params$sites,
    sort_by = "value",
    pod_lookup = get_pod_lookup(),
    tpma_lookup = reskit::get_tpma_label_lookup()
  ) |>
  reskit::make_tpma_impact_plot()
```

## Activity in detail

See [the model project information site][proj_gloss] for definitions of terms.

```{r}
#| label: pp-activity-in-detail-setup

tretspef_lookup <- reskit::get_tretspef_lookup()
horizon_year <- params$r$params[["end_year"]]


create_measure_label <- function(x) {
  x <- reskit:::uppercase_init(sub("dd", "d d", gsub("_", "-", x)))
  dplyr::if_else(x %in% c("Ambulance", "Walk-in"), paste(x, "arrivals"), x)
}

compile_da_data <- function(tbl, aggregation, pod_lookup, sites) {
  grp_cols <- c("pod", "measure", "sitetret", "model_run", "sex", aggregation)
  arr_cols <- c("pod", "measure", "sex", aggregation)
  tbl |>
    dplyr::mutate(
      dplyr::across("sex", reskit:::convert_sex_codes),
      dplyr::across("sex", \(x) forcats::fct(x, c("Female", "Male")))
    ) |>
    reskit:::calculate_principal_stats(grp_cols) |>
    reskit:::keep_mean_only() |>
    reskit:::filter_to_selected_sites(sites) |>
    reskit:::summarise_for_all_sites() |>
    dplyr::left_join(pod_lookup, "pod") |>
    dplyr::mutate(measure_label = create_measure_label(.data[["measure"]])) |>
    reskit:::add_change_cols() |>
    dplyr::arrange(dplyr::pick(tidyselect::all_of(arr_cols))) |>
    dplyr::select(!c("pod", "measure")) |>
    # as the two tables have different column names, we need to nest the data
    # so we can `list_rbind()` without error
    tidyr::nest(.by = tidyselect::ends_with("label"))
}
pt_compile_da_data <- purrr::partial(
  compile_da_data,
  # !! forces evaluation once on creation, not every run
  pod_lookup = !!get_pod_lookup(),
  sites = !!params$sites
)


make_da_table <- function(tbl, end_year) {
  tbl |>
    reskit::make_detailed_activity_table(end_year) |>
    gt::tab_options(table.align = "left")
}
pt_make_da_table <- purrr::partial(make_da_table, end_year = horizon_year)

handle_invalid_data <- function(tbl) {
  stopifnot(all(c("baseline", "principal", "change_pct") %in% colnames(tbl)))
  if (all(is.nan(tbl[["change_pct"]]))) {
    "Insufficient information to produce this table."
  } else if (all(c(tbl[["baseline"]], tbl[["principal"]]) == 0)) {
    "Insufficient information to produce this table."
  } else {
    tbl |>
      dplyr::mutate(dplyr::across("change_pct", \(x) {
        dplyr::case_when(
          all(c(.data[["baseline"]], .data[["principal"]]) == 0) ~ 0,
          is.nan(x) ~ NA_real_,
          .default = x
        )
      })) |>
      pt_make_da_table()
  }
}

detailed_activity_data <-
  list(
    age_group = reskit:::prepare_age_group_data(results),
    tretspef = reskit:::prepare_tretspef_data(results, tretspef_lookup)
  ) |>
  purrr::modify_at("age_group", \(x) pt_compile_da_data(x, "age_group")) |>
  purrr::modify_at("tretspef", \(x) pt_compile_da_data(x, "tretspef")) |>
  rlang::set_names(c("age group", "treatment specialty")) |>
  purrr::list_rbind(names_to = "aggregation") |>
  dplyr::mutate(
    chart_title = glue::glue("{measure_label} by {aggregation}"),
    .keep = "unused"
  ) |>
  tidyr::nest(.by = "activity_type_label") |>
  tibble::deframe() |>
  purrr::map(\(x) tibble::deframe(tidyr::nest(x, .by = "pod_label"))) |>
  purrr::map_depth(2, \(x) {
    tibble::deframe(tidyr::nest(x, .by = "chart_title"))
  }) |>
  purrr::map_depth(3, \(x) tidyr::unnest(x, "data"))
```

```{r}
#| label: detailed-activity-tables
#| results: asis

print_x <- \(x) if (is.character(x)) cat(x, "\n") else cat(knitr::knit_print(x))

detailed_activity_data |>
  purrr::iwalk(\(x, y) {
    cat("\n")
    cat("### ", y, "\n")
    purrr::iwalk(x, \(x, y) {
      cat("\n")
      cat("#### ", y, "\n")
      purrr::iwalk(x, \(x, y) {
        cat("\n")
        cat("##### ", y, "\n")
        print_x(handle_invalid_data(x))
        cat("\n")
      })
    })
  })
```


# Distribution of projections

## Activity summary

See [the model project information site][proj_gloss] for definitions of terms.

```{r}
#| label: dop-activity-summary

results |>
  reskit::compile_distribution_summary_data(
    value_type = "median",
    sites = params$sites,
    pod_lookup = get_pod_lookup()
  ) |>
  reskit::make_distribution_summary_table() |>
  gt::tab_options(table.width = gt::pct(100))
```

## Activity distribution

See [the model project information site][proj_gloss] for definitions of terms.

In 'beeswarm' plots (showing model-run distributions), the red vertical dashed
line is the principal value and the grey vertical continuous line is the
baseline value.

In 'S-curve' plots (showing empirical cumulative distribution function), the
red dashed line is the principal value, the blue dashed lines are the 10th and
90th percentiles and the grey vertical continuous line is the baseline value.

```{r}
#| label: distribution-plot-data-setup

# A customised version of reskit::compile_distribution_plot_data()
compile_distribution_plot_data <- function(results, pod_lookup, sites) {
  core_cols <- c("pod", "measure")
  group_cols <- c(core_cols, "model_run")
  arr_cols <- c("activity_type_label", core_cols)

  results |>
    purrr::pluck("default") |>
    reskit:::exclude_op_teleatt_procedures() |>
    reskit:::filter_to_selected_sites(sites) |>
    dplyr::select(!"sitetret") |>
    # sum across all (remaining) sites
    dplyr::summarise(dplyr::across("value", sum), .by = !"value") |>
    dplyr::mutate(
      stage = dplyr::if_else(.data[["model_run"]] == 0, "baseline", "principal")
    ) |>
    dplyr::mutate(
      mean = mean(.data[["value"]]),
      .by = tidyselect::all_of(reskit:::swap_modelrun_for_stage(group_cols))
    ) |>
    tidyr::pivot_wider(names_from = "stage", values_from = "mean") |>
    tidyr::fill("baseline", .by = tidyselect::all_of(core_cols)) |>
    dplyr::filter(dplyr::if_any("model_run", \(x) x > 0)) |>
    dplyr::mutate(measure_label = create_measure_label(.data[["measure"]])) |>
    reskit:::join_for_labels(pod_lookup) |>
    dplyr::arrange(dplyr::pick(tidyselect::all_of(arr_cols))) |>
    dplyr::select(!tidyselect::all_of(core_cols))
}
pt_compile_distribution_plot_data <- purrr::partial(
  compile_distribution_plot_data,
  # !! forces evaluation once on creation, not every time it's run
  pod_lookup = !!get_pod_lookup(),
  sites = !!params$sites
)

distribution_data <- results |>
  pt_compile_distribution_plot_data() |>
  tidyr::nest(.by = "activity_type_label") |>
  tibble::deframe() |>
  purrr::map(\(x) tibble::deframe(tidyr::nest(x, .by = "pod_label"))) |>
  purrr::map_depth(2, \(x) {
    tibble::deframe(tidyr::nest(x, .by = "measure_label"))
  })
```

```{r}
#| label: distribution-plots
#| results: asis

distribution_data |>
  purrr::iwalk(\(x, y) {
    cat("\n")
    cat("### ", y, "\n")
    purrr::iwalk(x, \(x, y) {
      cat("\n")
      cat("#### ", y, "\n")
      purrr::iwalk(x, \(x, y) {
        cat("\n")
        cat("##### ", y, "\n")
        knitr::knit_print(make_beeswarm_distrib_plot(x))
        cat("\n")
        knitr::knit_print(make_cumulative_distrib_plot(x))
        cat("\n")
      })
    })
  })
```
