---
title: "NHP Outputs Report (Extract B)"
output:
  html_document:
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
params:
  r: NA
  sites: NA
  wd: ".."
---

```{r}
#| label: setup
#| echo: false

knitr::opts_chunk$set(error = TRUE, echo = FALSE)
pkgload::load_all(params$wd, quiet = TRUE)
```

```{r}
#| label: site-selections
#| echo: false

sites_were_selected <- if (is.null(params$sites)) FALSE else TRUE

if (sites_were_selected) {
  site_status <- "selected sites"

  site_lookup <- yyjsonr::read_json_file(app_sys("app", "data", "sites.json"))
  sites_list <- site_lookup[params$sites]

  selected_sites <-
    paste0(sites_list, " (", names(sites_list), ")") |>
    sort() |>
    stringr::str_flatten(collapse = ", ", last = " and ")
} else {
  site_status <- selected_sites <- "all sites"
}
```

---
subtitle: "Scenario: `r params$r$params$scenario` (`r site_status`)"
---

# Notes

This report provides the outputs (tables and charts) from the selected model scenario (`r params$r$params$scenario`) for the following sites combined: `r selected_sites`.

Note that some tables and charts won't be generated if there was insufficient data to produce them, given the combination of trust and site selections (if any).

See [the project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information) for an overview of the model and its methodology.

# Metadata

This table shows the metadata for the selected model run:

```{r}
#| label: params-model-run

p <- get_params(params$r)
tabulate_model_run_info(p)
```

# Principal projection

## Summary

Bed-availability data is not available at site level. See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

```{r}
#| label: pp-summary

mod_principal_summary_data(params$r, params$sites) |>
  mod_principal_summary_table() |>
  gt::tab_options(table.align = "left")
```

## Length of stay summary

### Bed days

```{r}
#| label: pp-summary-los-beddays

mod_principal_summary_los_data(params$r, params$sites, "beddays") |>
  mod_principal_summary_los_table() |>
  gt::tab_options(table.align = "left")
```

### Admissions

```{r}
#| label: pp-summary-los-admissions

mod_principal_summary_los_data(params$r, params$sites, "admissions") |>
  mod_principal_summary_los_table() |>
  gt::tab_options(table.align = "left")
```

## Impact of changes

The results should be regarded as rough, high-level estimates of the number of rows added/removed due to each parameter. The plots here show results for all points of delivery combined. See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

```{r}
#| label: pp-impact-of-changes-setup

mitigator_lookup <- app_sys("app", "data", "mitigators.json") |>
  yyjsonr::read_json_file() |>
  purrr::simplify() |>
  tibble::enframe("strategy", "mitigator_name")

possibly_prep_principal_change_factors <-
  purrr::possibly(
    prep_principal_change_factors,
    "Insufficient data"
  )

pods <- get_activity_type_pod_measure_options() |>
  dplyr::distinct(activity_type, pod)

ip_pcf <- possibly_prep_principal_change_factors(
  data = params$r,
  sites = params$sites,
  mitigators = mitigator_lookup,
  at = "ip",
  pods = pods |> dplyr::filter(activity_type == "ip") |> dplyr::pull(pod)
)

op_pcf <- possibly_prep_principal_change_factors(
  data = params$r,
  sites = params$sites,
  mitigators = mitigator_lookup,
  at = "op",
  pods = pods |> dplyr::filter(activity_type == "op") |> dplyr::pull(pod)
)

aae_pcf <- possibly_prep_principal_change_factors(
  data = params$r,
  sites = params$sites,
  mitigators = mitigator_lookup,
  at = "aae",
  pods = pods |> dplyr::filter(activity_type == "aae") |> dplyr::pull(pod)
)
```

### Inpatients

#### Bed days

```{r}
#| label: pp-impact-of-changes-ip-bed-days

plot_impact_and_individual_change(ip_pcf, "beddays") |> purrr::walk(print)
```

#### Admissions

```{r}
#| label: pp-impact-of-changes-ip-admissions

plot_impact_and_individual_change(ip_pcf, "admissions") |> purrr::walk(print)
```

### Outpatients

#### Attendances

```{r}
#| label: pp-impact-of-changes-op-attendances

plot_impact_and_individual_change(op_pcf, "attendances") |> purrr::walk(print)
```

#### Tele-attendances

```{r}
#| label: pp-impact-of-changes-op-tele-attendances

plot_impact_and_individual_change(op_pcf, "tele_attendances") |>
  purrr::walk(print)
```

### A&E

#### Arrivals

```{r}
#| label: pp-impact-of-changes-aae-arrivals

plot_impact_and_individual_change(aae_pcf, "arrivals") |> purrr::walk(print)
```

## Activity in detail

See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

```{r}
#| label: pp-activity-in-detail-setup

tretspef_lookup <- yyjsonr::read_json_file(
  app_sys("app", "data", "tx-lookup.json")
) |>
  dplyr::mutate(
    dplyr::across("Description", \(x) stringr::str_remove(x, " Service$")),
    dplyr::across("Description", \(x) paste0(.data$Code, ": ", .data$Description)),
  ) |>
  dplyr::select(-"Group") |>
  dplyr::add_row(Code = "&", Description = "Not known") # as per HES dictionary

# Function to prepare data and table

possibly_generate_activity_in_detail_table <- purrr::possibly(
  generate_activity_in_detail_table,
  otherwise = "Insufficient information to produce this table"
)

# Prepare sets of inputs (activity, pods, measure, aggregation, sites)

atpmo_agg <- get_activity_type_pod_measure_options() |>
  dplyr::select("activity_type", "pod", "measure" = "measures") |>
  tidyr::crossing(agg_col = c("age_group", "tretspef")) |>
  dplyr::mutate(
    activity_type = dplyr::case_match(
      activity_type,
      "ip" ~ "inpatients",
      "op" ~ "outpatients",
      "aae" ~ "aae"
    )
  )

activity_in_detail_table_names <- atpmo_agg |>
  dplyr::mutate(table_name = paste(pod, measure, agg_col, sep = "_")) |>
  dplyr::pull()

# Prepare a list with each set of input combos

activity_in_detail_tables <- purrr::pmap(
  atpmo_agg,
  \(activity_type, pod, measure, agg_col) {
    possibly_generate_activity_in_detail_table(
      data = params$r,
      sites = params$sites,
      tretspefs = tretspef_lookup,
      activity_type,
      pod,
      measure,
      agg_col
    )
  }
) |>
  purrr::set_names(activity_in_detail_table_names)
```

### Inpatients

#### Non-elective admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-1

activity_in_detail_tables$`ip_non-elective_admission_beddays_age_group`
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-2

activity_in_detail_tables$`ip_non-elective_admission_beddays_tretspef`
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-3

activity_in_detail_tables$`ip_non-elective_admission_admissions_age_group`
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-4

activity_in_detail_tables$`ip_non-elective_admission_admissions_tretspef`
```

#### Elective admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-5

activity_in_detail_tables$ip_elective_admission_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-6

activity_in_detail_tables$ip_elective_admission_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-7

activity_in_detail_tables$ip_elective_admission_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-8

activity_in_detail_tables$ip_elective_admission_admissions_tretspef
```

#### Daycase admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-9

activity_in_detail_tables$ip_elective_daycase_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-10

activity_in_detail_tables$ip_elective_daycase_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-11

activity_in_detail_tables$ip_elective_daycase_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-12

activity_in_detail_tables$ip_elective_daycase_admissions_tretspef
```

#### Maternity admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-13

activity_in_detail_tables$ip_maternity_admission_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-14

activity_in_detail_tables$ip_maternity_admission_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-15

activity_in_detail_tables$ip_maternity_admission_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-16

activity_in_detail_tables$ip_maternity_admission_admissions_tretspef
```

#### Regular day attender admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-17

activity_in_detail_tables$ip_regular_day_attender_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-18

activity_in_detail_tables$ip_regular_day_attender_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-19

activity_in_detail_tables$ip_regular_day_attender_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-20

activity_in_detail_tables$ip_regular_day_attender_admissions_tretspef
```

#### Regular night attender admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-21

activity_in_detail_tables$ip_regular_night_attender_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-22

activity_in_detail_tables$ip_regular_night_attender_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-23

activity_in_detail_tables$ip_regular_night_attender_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-24

activity_in_detail_tables$ip_regular_night_attender_admissions_tretspef
```



### Outpatients

#### First oupatient attendance

##### Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-1

activity_in_detail_tables$op_first_attendances_age_group
```

##### Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-2

activity_in_detail_tables$op_first_attendances_tretspef
```

##### Tele-attendances by age group

```{r}
#| label: pp-activity-in-detail-op-3

activity_in_detail_tables$op_first_tele_attendances_age_group
```

##### Tele-attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-4

activity_in_detail_tables$op_first_tele_attendances_tretspef
```

#### Follow-up outpatient attendance

##### Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-5

activity_in_detail_tables$`op_follow-up_attendances_age_group`
```

##### Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-6

activity_in_detail_tables$`op_follow-up_attendances_tretspef`
```

##### Tele-attendances by age group

```{r}
#| label: pp-activity-in-detail-op-7

activity_in_detail_tables$`op_follow-up_tele_attendances_age_group`
```

##### Tele-attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-8

activity_in_detail_tables$`op_follow-up_tele_attendances_tretspef`
```

#### Outpatient procedure

##### Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-9

activity_in_detail_tables$op_procedure_attendances_age_group
```

##### Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-10

activity_in_detail_tables$op_procedure_attendances_tretspef
```

### A&E

#### Type 1 department

##### Ambulance arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-1

activity_in_detail_tables$`aae_type-01_ambulance_age_group`
```

##### Walk-in arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-3

activity_in_detail_tables$`aae_type-01_walk-in_age_group`
```

#### Type 2 department

##### Ambulance arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-5

activity_in_detail_tables$`aae_type-02_ambulance_age_group`
```

##### Walk-in arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-7

activity_in_detail_tables$`aae_type-02_walk-in_age_group`
```

#### Type 3 department

##### Ambulance arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-9

activity_in_detail_tables$`aae_type-03_ambulance_age_group`
```

##### Walk-in arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-11

activity_in_detail_tables$`aae_type-03_walk-in_age_group`
```

#### Type 4 department

##### Ambulance arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-13

activity_in_detail_tables$`aae_type-04_ambulance_age_group`
```

##### Walk-in arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-15

activity_in_detail_tables$`aae_type-04_walk-in_age_group`
```

# Distribution of projections

## Activity summary

See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

```{r}
#| label: dop-activity-summary

atpmo <- get_activity_type_pod_measure_options()

params$r |>
  get_model_core_activity(params$sites) |>
  dplyr::inner_join(atpmo, by = c("pod", "measure" = "measures")) |>
  mod_model_core_activity_server_table() |>
  gt::tab_options(table.width = gt::pct(100))
```

## Activity distribution

See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

In 'beeswarm' plots (showing model-run distributions), the red vertical dashed line is the principal value and the grey vertical continuous line is the baseline value.

In 'S-curve' plots (showing empirical cumulative distribution function), the red dashed line is the principal value, the blue dashed lines are the 10th and 90th percentiles and the grey vertical continuous line is the baseline value.

```{r}
#| label: dop-activity-distribution-setup

# Prepare sets of inputs (activity, pods, measure, aggregation, sites)

atpmo_simplified <- get_activity_type_pod_measure_options() |>
  dplyr::select("activity_type", "pod", "measure" = "measures") |>
  dplyr::mutate(
    activity_type = dplyr::case_match(
      activity_type, "ip" ~ "inpatients", "op" ~ "outpatients", "aae" ~ "aae"
    )
  )

activity_distribution_table_names <- atpmo_simplified |>
  dplyr::mutate(table_name = paste(pod, measure, sep = "_")) |>
  dplyr::pull()

# Prepare a list of plots with each set of input combos

possibly_plot_activity_distributions <- purrr::possibly(
  plot_activity_distributions,
  otherwise = "Insufficient information to produce this chart"
)

activity_distributions <- atpmo_simplified |>
  purrr::pmap(
    \(activity_type, pod, measure) {
      possibly_plot_activity_distributions(
        data = params$r, sites = params$sites, activity_type, pod, measure
      )
    }
  ) |>
  purrr::set_names(activity_distribution_table_names)
```

### Inpatients

#### Non-elective admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-1

activity_distributions$`ip_non-elective_admission_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-2

activity_distributions$`ip_non-elective_admission_admissions` |>
  purrr::walk(print)
```

#### Elective admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-3

activity_distributions$`ip_elective_admission_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-4

activity_distributions$`ip_elective_admission_admissions` |> purrr::walk(print)
```

#### Daycase admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-5

activity_distributions$`ip_daycase_admission_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-6

activity_distributions$`ip_daycase_admission_admissions` |> purrr::walk(print)
```

#### Maternity admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-7

activity_distributions$`ip_maternity_admission_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-8

activity_distributions$`ip_maternity_admission_admissions` |> purrr::walk(print)
```

#### Regular day attender admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-9

activity_distributions$`ip_regular_day_attender_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-10

activity_distributions$`ip_regular_day_attender_admissions` |> purrr::walk(print)
```

#### Regular night attender admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-11

activity_distributions$`ip_regular_night_attender_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-12

activity_distributions$`ip_regular_night_attender_admissions` |> purrr::walk(print)
```

### Outpatients

#### First outpatient attendance

##### Attendances

```{r}
#| label: pp-activity-distribution-op-1

activity_distributions$`op_first_attendances` |> purrr::walk(print)
```

##### Tele-attendances

```{r}
#| label: pp-activity-distribution-op-2

activity_distributions$`op_first_tele_attendances` |> purrr::walk(print)
```

#### Follow-up outpatient attendances

##### Attendances

```{r}
#| label: pp-activity-distribution-op-3

activity_distributions$`op_follow-up_attendances` |> purrr::walk(print)
```

##### Tele-attendances

```{r}
#| label: pp-activity-distribution-op-4

activity_distributions$`op_follow-up_tele_attendances` |> purrr::walk(print)
```

#### Outpatient procedures

##### Attendances

```{r}
#| label: pp-activity-distribution-op-5

activity_distributions$`op_outpatient_attendances` |> purrr::walk(print)
```

##### Tele-attendances

```{r}
#| label: pp-activity-distribution-op-6

activity_distributions$`op_outpatient_tele_attendances` |> purrr::walk(print)
```

### A&E

#### Type 1 department

##### Walk-in arrivals

```{r}
#| label: pp-activity-distribution-aae-1

activity_distributions$`aae_type-01_walk-in` |> purrr::walk(print)
```

##### Ambulance arrivals

```{r}
#| label: pp-activity-distribution-aae-2

activity_distributions$`aae_type-01_ambulance` |> purrr::walk(print)
```

#### Type 2 department

##### Walk-in arrivals

```{r}
#| label: pp-activity-distribution-aae-3

activity_distributions$`aae_type-02_walk-in` |> purrr::walk(print)
```

##### Ambulance arrivals

```{r}
#| label: pp-activity-distribution-aae-4

activity_distributions$`aae_type-02_ambulance` |> purrr::walk(print)
```

#### Type 3 department

##### Walk-in arrivals

```{r}
#| label: pp-activity-distribution-aae-5

activity_distributions$`aae_type-03_walk-in` |> purrr::walk(print)
```

##### Ambulance arrivals

```{r}
#| label: pp-activity-distribution-aae-6

activity_distributions$`aae_type-03_ambulance` |> purrr::walk(print)
```

#### Type 4 department

##### Walk-in arrivals

```{r}
#| label: pp-activity-distribution-aae-7

activity_distributions$`aae_type-04_walk-in` |> purrr::walk(print)
```

##### Ambulance arrivals

```{r}
#| label: pp-activity-distribution-aae-8

activity_distributions$`aae_type-04_ambulance` |> purrr::walk(print)
```
