---
title: NHP outputs report
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: true
params:
  r: NA
---

```{r}
#| label: params-model-run
#| echo: FALSE

knitr::opts_chunk$set(error = TRUE, echo = FALSE)

r <- params$r
p <- get_params(r)
```

This is model run `r params$r$params$id`.

## Input parameters

### Model run

```{r}
#| label: params-model-run

```

### Demographic adjusment

```{r}
#| label: params-demographic-adjustment

info_params_table_demographic_adjustment(p)
```

### Baseline adjustment

```{r}
#| label: params-baseline-adjustment

info_params_table_baseline_adjustment(p)
```

### Covid adjustment

```{r}
#| label: params-covid-adjustment

info_params_table_covid_adjustment(p)
```

### Waiting list adjustment

```{r}
#| label: params-waiting-list-adjustment

info_params_table_waiting_list_adjustment(p)
```

### Expat

```{r}
#| label: params-expat

info_params_table_expat_repat_adjustment(p, "expat")
```

### Repat (local)

```{r}
#| label: params-repat-local

info_params_table_expat_repat_adjustment(p, "repat_local")
```

### Repat (non-local)

```{r}
#| label: params-repat-non-local

info_params_table_expat_repat_adjustment(p, "repat_nonlocal")
```

### Non-demographic adjustment

```{r}
#| label: params-non-demographic-adjustment

info_params_table_non_demographic_adjustment(p)
```

### Activity avoidance

```{r}
#| label: params-activity-avoidance

info_params_table_activity_avoidance(p)
```

### Efficiencies

```{r}
#| label: params-efficiencies

info_params_table_efficiencies(p)
```

### Bed occupancy

```{r}
#| label: params-bed-occupancy-day-night

info_params_table_bed_occupancy_day_night(p)
```

```{r}
#| label: params-bed-occupancy-specialty-mapping

info_params_table_bed_occupancy_specialty_mapping(p)
```

## Outputs

### Principal projection

#### Summary

```{r}
#| label: pp-summary

```

#### Impact of changes

```{r}
#| label: pp-impact-of-changes

```

#### Summary by year

```{r}
#| label: pp-summary-by-year

```

#### Activity in detail

```{r}
#| label: pp-activity-in-detail

```

### Distribution of projections

#### Activity summary

```{r}
#| label: dop-activity-summary

```

#### Activity distribution

```{r}
#| label: dop-activity-distribution

```
