---
title: "NHP Outputs Report (Extract B)"
output:
  html_document:
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
params:
  r: NA
  sites: NA
---

```{r}
#| label: setup
#| echo: false

knitr::opts_chunk$set(error = TRUE, echo = FALSE, out.width = "100%")

library(reskit)
```

```{r}
#| label: site-selections
#| echo: false

sites_were_selected <- if (is.null(params$sites)) FALSE else TRUE

if (sites_were_selected) {
  site_status <- "selected sites"

  site_lookup <- yyjsonr::read_json_file(app_sys("app", "data", "sites.json"))
  sites_list <- site_lookup[params$sites]

  selected_sites <-
    paste0(sites_list, " (", names(sites_list), ")") |>
    sort() |>
    stringr::str_flatten(collapse = ", ", last = " and ")
} else {
  site_status <- selected_sites <- "all sites"
}
```

---
subtitle: "Scenario: `r params$r$params$scenario` (`r site_status`)"
---

# Notes

This report provides the outputs (tables and charts) from the selected model scenario (`r params$r$params$scenario`) for the following sites combined: `r selected_sites`.

Note that some tables and charts won't be generated if there was insufficient data to produce them, given the combination of trust and site selections (if any).

This document is produced dynamically and so plots may not be produced at optimal size.
Please [contact The Strategy Unit Data Science team](mailto:mlcsu.su.datascience@nhs.net) if this is a problem.

See [the project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information) for an overview of the model and its methodology.

# Metadata

This table shows the metadata for the selected model run:

```{r}
#| label: params-model-run

p <- get_params(params$r)
tabulate_model_run_info(p)
```

# Principal projection

## Summary

Bed-availability data is not available at site level. See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

```{r}
#| label: pp-summary

params$r$results |>
  reskit::compile_principal_pod_data(
    sites = params$sites,
    pod_lookup = reskit::get_principal_pods()
  ) |>
  reskit::make_principal_pod_table() |>
  gt::tab_options(table.align = "left")
```

## Length of stay summary

### Bed days

```{r}
#| label: pp-summary-los-beddays

params$r$results |>
  reskit::compile_principal_los_data(
    measure = "beddays",
    sites = params$sites,
    pod_lookup = get_pod_lookup()
  ) |>
  reskit::make_principal_los_table() |>
  gt::tab_options(table.align = "left")
```

### Admissions

```{r}
#| label: pp-summary-los-admissions

params$r$results |>
  reskit::compile_principal_los_data(
    measure = "admissions",
    sites = params$sites,
    pod_lookup = get_pod_lookup()
  ) |>
  reskit::make_principal_los_table() |>
  gt::tab_options(table.align = "left")
```

## Impact of changes

The results should be regarded as rough, high-level estimates of the number of rows added/removed due to each parameter. The plots here show results for all points of delivery combined. See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

```{r}
#| label: pp-impact-of-changes-setup

# Stopgap values so the ICF chart content is visible, see:
# https://github.com/The-Strategy-Unit/nhp_outputs/issues/427
icf_fig_height <- 7
icf_font_size <- 10

# Return a useful message if the data is empty, see:
# https://github.com/The-Strategy-Unit/nhp_outputs/issues/441
make_icf_chart_or_msg <- function(icf_data) {
  if (nrow(icf_data) == 0) {
    "Insufficient information to produce this chart."
  } else {
    icf_data |>
      reskit::make_individual_cf_plot() +
      ggplot2::theme(text = ggplot2::element_text(size = icf_font_size))
  }
}
```

### Inpatients

#### Bed days

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-ip-bed-days

params$r$results |>
  reskit::compile_change_factor_data(
    measure = "beddays",
    activity_type = "ip",
    sites = params$sites,
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  reskit::make_overall_cf_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-ip-bed-days

params$r$results |>
  reskit::compile_indiv_change_factor_data(
    measure = "beddays",
    activity_type = "ip",
    sites = params$sites,
    sort_by = "value",
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  make_icf_chart_or_msg()
```

#### Admissions

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-ip-admissions

params$r$results |>
  reskit::compile_change_factor_data(
    measure = "admissions",
    activity_type = "ip",
    sites = params$sites,
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  reskit::make_overall_cf_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-ip-admissions

params$r$results |>
  reskit::compile_indiv_change_factor_data(
    measure = "admissions",
    activity_type = "ip",
    sites = params$sites,
    sort_by = "value",
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  make_icf_chart_or_msg()
```

### Outpatients

#### Attendances

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-op-attendances

params$r$results |>
  reskit::compile_change_factor_data(
    measure = "attendances",
    activity_type = "op",
    sites = params$sites,
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  reskit::make_overall_cf_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-op-attendances

params$r$results |>
  reskit::compile_indiv_change_factor_data(
    measure = "attendances",
    activity_type = "op",
    sites = params$sites,
    sort_by = "value",
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  make_icf_chart_or_msg()
```

#### Tele-attendances

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-op-tele-attendances

params$r$results |>
  reskit::compile_change_factor_data(
    measure = "tele_attendances",
    activity_type = "op",
    sites = params$sites,
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  reskit::make_overall_cf_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-op-tele-attendances

params$r$results |>
  reskit::compile_indiv_change_factor_data(
    measure = "tele_attendances",
    activity_type = "op",
    sites = params$sites,
    sort_by = "value",
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  make_icf_chart_or_msg()
```

### A&E

#### Arrivals

##### Overall change-factors

```{r}
#| label: pp-impact-of-changes-overall-aae-arrivals

params$r$results |>
  reskit::compile_change_factor_data(
    measure = "arrivals",
    activity_type = "aae",
    sites = params$sites,
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  reskit::make_overall_cf_plot()
```

##### Individual change-factors

```{r, fig.height=icf_fig_height}
#| label: pp-impact-of-changes-individual-aae-arrivals

params$r$results |>
  reskit::compile_indiv_change_factor_data(
    measure = "arrivals",
    activity_type = "aae",
    sites = params$sites,
    sort_by = "value",
    tpma_lookup = reskit::get_tpma_label_lookup(),
    pod_lookup = reskit::get_principal_pods()
  ) |>
  make_icf_chart_or_msg()
```

## Activity in detail

See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

```{r}
#| label: pp-activity-in-detail-setup

# Prepare sets of inputs (activity, pods, measure, aggregation, sites)

pod_lookup <- reskit::get_detailed_pods()
end_year <- params[["end_year"]]

age_group_data <- list(
  "sex+age_group" = params$r$results[["sex+age_group"]] |>
    reskit:::filter_to_selected_sites(params$sites) |>
    dplyr::mutate(
      value_type = ifelse(.data[["model_run"]] == 0, "baseline", "principal")
    ) |>
    dplyr::summarise(
      dplyr::across("value", mean),
      .by = -c("model_run", "value", "sitetret")
    ) |>
    tidyr::pivot_wider(
      names_from = "value_type",
      values_from = "value"
    )
) |>
  reskit:::prepare_age_group_data()

tretspef_data <- list(
  "sex+tretspef_grouped" = params$r$results[["sex+tretspef_grouped"]] |>
    reskit:::filter_to_selected_sites(params$sites) |>
    dplyr::mutate(
      value_type = ifelse(.data[["model_run"]] == 0, "baseline", "principal")
    ) |>
    dplyr::summarise(
      dplyr::across("value", mean),
      .by = -c("model_run", "value", "sitetret")
    ) |>
    tidyr::pivot_wider(
      names_from = "value_type",
      values_from = "value"
    )
) |>
  reskit:::prepare_tretspef_data(reskit::get_tretspef_lookup())

activity_in_detail_tables <- list("age_group" = age_group_data, "tretspef" = tretspef_data) |>
  purrr::imap(\(.x, .i) {
    .x |>
      dplyr::mutate(dplyr::across("sex", \(.x) forcats::fct(ifelse(.x == 1, "Male", "Female")))) |>
      dplyr::group_nest(measure, pod) |>
      reskit:::get_activity_type_from_pod() |>
      reskit:::inner_join_for_labels(pod_lookup) |>
      reskit:::relabel_pods() |>
      dplyr::mutate(agg_col = .i) |>
      dplyr::mutate(table_name = paste(pod, measure, agg_col, sep = "_")) |>
      dplyr::select("table_name", "data") |>
      tibble::deframe()
  }) |>
  purrr::list_flatten() |>
  purrr::map(
    \(.x) {
      .x |>
        dplyr::mutate(
          change = .data[["principal"]] - .data[["baseline"]],
          change_pct = .data[["change"]] / .data[["baseline"]]
        ) |>
        reskit::make_detailed_activity_table(final_year = end_year) |>
        gt::tab_options(table.align = "left")
    }
  )
```

### Inpatients

#### Non-elective admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-1

activity_in_detail_tables$`ip_non-elective_admission_beddays_age_group`
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-2

activity_in_detail_tables$`ip_non-elective_admission_beddays_tretspef`
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-3

activity_in_detail_tables$`ip_non-elective_admission_admissions_age_group`
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-4

activity_in_detail_tables$`ip_non-elective_admission_admissions_tretspef`
```

#### Elective admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-5

activity_in_detail_tables$ip_elective_admission_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-6

activity_in_detail_tables$ip_elective_admission_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-7

activity_in_detail_tables$ip_elective_admission_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-8

activity_in_detail_tables$ip_elective_admission_admissions_tretspef
```

#### Daycase admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-9

activity_in_detail_tables$ip_elective_daycase_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-10

activity_in_detail_tables$ip_elective_daycase_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-11

activity_in_detail_tables$ip_elective_daycase_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-12

activity_in_detail_tables$ip_elective_daycase_admissions_tretspef
```

#### Maternity admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-13

activity_in_detail_tables$ip_maternity_admission_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-14

activity_in_detail_tables$ip_maternity_admission_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-15

activity_in_detail_tables$ip_maternity_admission_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-16

activity_in_detail_tables$ip_maternity_admission_admissions_tretspef
```

#### Regular day attender admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-17

activity_in_detail_tables$ip_regular_day_attender_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-18

activity_in_detail_tables$ip_regular_day_attender_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-19

activity_in_detail_tables$ip_regular_day_attender_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-20

activity_in_detail_tables$ip_regular_day_attender_admissions_tretspef
```

#### Regular night attender admission

##### Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-21

activity_in_detail_tables$ip_regular_night_attender_beddays_age_group
```

##### Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-22

activity_in_detail_tables$ip_regular_night_attender_beddays_tretspef
```

##### Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-23

activity_in_detail_tables$ip_regular_night_attender_admissions_age_group
```

##### Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-24

activity_in_detail_tables$ip_regular_night_attender_admissions_tretspef
```



### Outpatients

#### First oupatient attendance

##### Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-1

activity_in_detail_tables$op_first_attendances_age_group
```

##### Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-2

activity_in_detail_tables$op_first_attendances_tretspef
```

##### Tele-attendances by age group

```{r}
#| label: pp-activity-in-detail-op-3

activity_in_detail_tables$op_first_tele_attendances_age_group
```

##### Tele-attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-4

activity_in_detail_tables$op_first_tele_attendances_tretspef
```

#### Follow-up outpatient attendance

##### Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-5

activity_in_detail_tables$`op_follow-up_attendances_age_group`
```

##### Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-6

activity_in_detail_tables$`op_follow-up_attendances_tretspef`
```

##### Tele-attendances by age group

```{r}
#| label: pp-activity-in-detail-op-7

activity_in_detail_tables$`op_follow-up_tele_attendances_age_group`
```

##### Tele-attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-8

activity_in_detail_tables$`op_follow-up_tele_attendances_tretspef`
```

#### Outpatient procedure

##### Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-9

activity_in_detail_tables$op_procedure_attendances_age_group
```

##### Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-10

activity_in_detail_tables$op_procedure_attendances_tretspef
```

### A&E

#### Type 1 department

##### Ambulance arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-1

activity_in_detail_tables$`aae_type-01_ambulance_age_group`
```

##### Walk-in arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-3

activity_in_detail_tables$`aae_type-01_walk-in_age_group`
```

#### Type 2 department

##### Ambulance arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-5

activity_in_detail_tables$`aae_type-02_ambulance_age_group`
```

##### Walk-in arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-7

activity_in_detail_tables$`aae_type-02_walk-in_age_group`
```

#### Type 3 department

##### Ambulance arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-9

activity_in_detail_tables$`aae_type-03_ambulance_age_group`
```

##### Walk-in arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-11

activity_in_detail_tables$`aae_type-03_walk-in_age_group`
```

#### Type 4 department

##### Ambulance arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-13

activity_in_detail_tables$`aae_type-04_ambulance_age_group`
```

##### Walk-in arrivals by age group

```{r}
#| label: pp-activity-in-detail-aae-15

activity_in_detail_tables$`aae_type-04_walk-in_age_group`
```

# Distribution of projections

## Activity summary

See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

```{r}
#| label: dop-activity-summary

params$r$results |>
  reskit::compile_distribution_summary_data(
    value_type = "median",
    sites = params$sites,
    pod_lookup = get_pod_lookup()
  ) |>
  reskit::make_distribution_summary_table() |>
  gt::tab_options(table.width = gt::pct(100))
```

## Activity distribution

See [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information/user_guide/glossary.html) for definitions of terms.

In 'beeswarm' plots (showing model-run distributions), the red vertical dashed line is the principal value and the grey vertical continuous line is the baseline value.

In 'S-curve' plots (showing empirical cumulative distribution function), the red dashed line is the principal value, the blue dashed lines are the 10th and 90th percentiles and the grey vertical continuous line is the baseline value.

```{r}
#| label: dop-activity-distribution-setup

# Prepare sets of inputs (activity, pods, measure, aggregation, sites)

atpmo_simplified <- get_activity_type_pod_measure_options() |>
  dplyr::select("activity_type", "pod", "measure" = "measures")

activity_distribution_table_names <- atpmo_simplified |>
  dplyr::mutate(table_name = paste(pod, measure, sep = "_")) |>
  dplyr::pull()

# Prepare a list of plots with each set of input combos

possibly_plot_activity_distributions <- purrr::possibly(
  plot_activity_distributions,
  otherwise = "Insufficient information to produce this chart"
)

activity_distributions <- atpmo_simplified |>
  purrr::pmap(
    \(activity_type, pod, measure) {
      possibly_plot_activity_distributions(
        data = params$r, sites = params$sites, activity_type, pod, measure
      )
    }
  ) |>
  purrr::set_names(activity_distribution_table_names)
```

### Inpatients

#### Non-elective admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-1

activity_distributions$`ip_non-elective_admission_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-2

activity_distributions$`ip_non-elective_admission_admissions` |>
  purrr::walk(print)
```

#### Elective admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-3

activity_distributions$`ip_elective_admission_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-4

activity_distributions$`ip_elective_admission_admissions` |> purrr::walk(print)
```

#### Daycase admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-5

activity_distributions$`ip_daycase_admission_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-6

activity_distributions$`ip_daycase_admission_admissions` |> purrr::walk(print)
```

#### Maternity admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-7

activity_distributions$`ip_maternity_admission_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-8

activity_distributions$`ip_maternity_admission_admissions` |> purrr::walk(print)
```

#### Regular day attender admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-9

activity_distributions$`ip_regular_day_attender_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-10

activity_distributions$`ip_regular_day_attender_admissions` |> purrr::walk(print)
```

#### Regular night attender admission

##### Bed days

```{r}
#| label: pp-activity-distribution-ip-11

activity_distributions$`ip_regular_night_attender_beddays` |> purrr::walk(print)
```

##### Admissions

```{r}
#| label: pp-activity-distribution-ip-12

activity_distributions$`ip_regular_night_attender_admissions` |> purrr::walk(print)
```

### Outpatients

#### First outpatient attendance

##### Attendances

```{r}
#| label: pp-activity-distribution-op-1

activity_distributions$`op_first_attendances` |> purrr::walk(print)
```

##### Tele-attendances

```{r}
#| label: pp-activity-distribution-op-2

activity_distributions$`op_first_tele_attendances` |> purrr::walk(print)
```

#### Follow-up outpatient attendances

##### Attendances

```{r}
#| label: pp-activity-distribution-op-3

activity_distributions$`op_follow-up_attendances` |> purrr::walk(print)
```

##### Tele-attendances

```{r}
#| label: pp-activity-distribution-op-4

activity_distributions$`op_follow-up_tele_attendances` |> purrr::walk(print)
```

#### Outpatient procedures

##### Attendances

```{r}
#| label: pp-activity-distribution-op-5

activity_distributions$`op_outpatient_attendances` |> purrr::walk(print)
```

##### Tele-attendances

```{r}
#| label: pp-activity-distribution-op-6

activity_distributions$`op_outpatient_tele_attendances` |> purrr::walk(print)
```

### A&E

#### Type 1 department

##### Walk-in arrivals

```{r}
#| label: pp-activity-distribution-aae-1

activity_distributions$`aae_type-01_walk-in` |> purrr::walk(print)
```

##### Ambulance arrivals

```{r}
#| label: pp-activity-distribution-aae-2

activity_distributions$`aae_type-01_ambulance` |> purrr::walk(print)
```

#### Type 2 department

##### Walk-in arrivals

```{r}
#| label: pp-activity-distribution-aae-3

activity_distributions$`aae_type-02_walk-in` |> purrr::walk(print)
```

##### Ambulance arrivals

```{r}
#| label: pp-activity-distribution-aae-4

activity_distributions$`aae_type-02_ambulance` |> purrr::walk(print)
```

#### Type 3 department

##### Walk-in arrivals

```{r}
#| label: pp-activity-distribution-aae-5

activity_distributions$`aae_type-03_walk-in` |> purrr::walk(print)
```

##### Ambulance arrivals

```{r}
#| label: pp-activity-distribution-aae-6

activity_distributions$`aae_type-03_ambulance` |> purrr::walk(print)
```

#### Type 4 department

##### Walk-in arrivals

```{r}
#| label: pp-activity-distribution-aae-7

activity_distributions$`aae_type-04_walk-in` |> purrr::walk(print)
```

##### Ambulance arrivals

```{r}
#| label: pp-activity-distribution-aae-8

activity_distributions$`aae_type-04_ambulance` |> purrr::walk(print)
```
