---
title: NHP Outputs Report 
output:
  html_document:
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
params:
  r: NA
  sites: NA
---

```{css, echo=FALSE}
h1 {
font-size: 32px;
}

h2 {
  font-size: 28px;
}

h3 {
  font-size: 26px;
}

h4 {
  font-size: 24px;
}

h5 {
  font-size: 22px;
}

h6 {
  font-size: 20px;
}

p {
  font-size: 16px;
}
```

```{r}
#| label: setup
#| echo: FALSE

knitr::opts_chunk$set(error = TRUE, echo = FALSE)

r <- params$r
p <- get_params(r)
```

```{r}
#| label: site-selections

sites_were_selected <- if (is.null(params$sites)) FALSE else TRUE

selected_sites <- if (sites_were_selected) {
  paste(params$sites, collapse = ", ")
} else {
  "all"
}
```

---
subtitle: Model run `r p$id` with `r selected_sites` sites selected
---

## Notes

Further information about the model and these results can be found on [the model project information site](https://connect.strategyunitwm.nhs.uk/nhp/project_information).

Some data is presented at trust level even if you made a site selection in the app. This is noted in the relevant sections below.

Some sections will not contain charts and data if they weren't supplied or if there's insufficient data.

This report reflects the site selections made in the app before the 'donwload report' button was clicked. The site selections for this report are: `r htmltools::strong(selected_sites)`.

## Input parameters

### Model run

```{r}
#| label: params-model-run

p_model_run <- purrr::keep(p, rlang::is_atomic)

p_model_run[["start_year"]] <- scales::number(
  p_model_run[["start_year"]] + ((p_model_run[["start_year"]] + 1) %% 100) / 100,
  0.01,
  big.mark = "", decimal.mark = "/"
)
p_model_run[["end_year"]] <- scales::number(
  p_model_run[["end_year"]] + ((p_model_run[["end_year"]] + 1) %% 100) / 100,
  0.01,
  big.mark = "",
  decimal.mark = "/"
)

p_model_run[["create_datetime"]] <- p_model_run[["create_datetime"]] |>
  lubridate::fast_strptime("%Y%m%d_%H%M%S") |>
  format("%d-%b-%Y %H:%M:%S")

p_model_run |>
  unlist() |>
  tibble::enframe() |> 
  gt::gt("name") |> 
  gt_theme() |> 
  gt::tab_options(table.align = "left")
```

### Demographic adjustment

```{r}
#| label: params-demographic-adjustment

info_params_table_demographic_adjustment(p) |> 
  gt::tab_options(table.align = "left")
```

### Baseline adjustment

```{r}
#| label: params-baseline-adjustment

info_params_table_baseline_adjustment(p) |> 
  gt::tab_options(table.align = "left")
```

### Covid adjustment

```{r}
#| label: params-covid-adjustment

info_params_table_covid_adjustment(p) |> 
  gt::tab_options(table.align = "left")
```

### Waiting list adjustment

```{r}
#| label: params-waiting-list-adjustment

info_params_table_waiting_list_adjustment(p) |> 
  gt::tab_options(table.align = "left")
```

### Expat

```{r}
#| label: params-expat

info_params_table_expat_repat_adjustment(p, "expat") |> 
  gt::tab_options(table.align = "left")
```

### Repat (local)

```{r}
#| label: params-repat-local

info_params_table_expat_repat_adjustment(p, "repat_local") |> 
  gt::tab_options(table.align = "left")
```

### Repat (non-local)

```{r}
#| label: params-repat-non-local

info_params_table_expat_repat_adjustment(p, "repat_nonlocal") |> 
  gt::tab_options(table.align = "left")
```

### Non-demographic adjustment

```{r}
#| label: params-non-demographic-adjustment

info_params_table_non_demographic_adjustment(p) |> 
  gt::tab_options(table.align = "left")
```

### Activity avoidance

```{r}
#| label: params-activity-avoidance

info_params_table_activity_avoidance(p) |> 
  gt::tab_options(table.align = "left")
```

### Efficiencies

```{r}
#| label: params-efficiencies

info_params_table_efficiencies(p) |> 
  gt::tab_options(table.align = "left")
```

### Bed occupancy

```{r}
#| label: params-bed-occupancy-day-night

info_params_table_bed_occupancy_day_night(p) |> 
  gt::tab_options(table.align = "left")
```

```{r}
#| label: params-bed-occupancy-specialty-mapping

info_params_table_bed_occupancy_specialty_mapping(p) |> 
  gt::tab_options(table.align = "left")
```

## Outputs

### Principal projection

#### Summary

```{r}
#| label: pp-summary

mod_principal_summary_data(r, params$sites) |> 
  mod_principal_summary_table()
```

#### Impact of changes

```{r}
#| label: pp-impact-of-changes-setup

prep_principal_change_factors <- function(data, at, mitigator_lookup) {
  
  data |> 
    get_principal_change_factors(at) |>
    dplyr::mutate(
      dplyr::across("change_factor", forcats::fct_inorder),
      dplyr::across(
        "change_factor",
        \(.x) forcats::fct_relevel(
          .x, 
          "baseline", 
          "demographic_adjustment", 
          "health_status_adjustment"
        )
      )
    ) |>
    dplyr::left_join(
      mitigator_lookup,
      by = dplyr::join_by("strategy")
    ) |>
    tidyr::replace_na(list("mitigator_name" = "-"))
  
}

mitigator_lookup <- app_sys("app", "data", "mitigators.json") |>
  jsonlite::read_json(simplifyVector = TRUE) |>
  purrr::simplify() |>
  tibble::enframe("strategy", "mitigator_name")

ip_pcf  <- prep_principal_change_factors(params$r, "ip",  mitigator_lookup) 
op_pcf  <- prep_principal_change_factors(params$r, "op",  mitigator_lookup) 
aae_pcf <- prep_principal_change_factors(params$r, "aae", mitigator_lookup) 
```

##### Inpatients

###### Bed days

```{r}
#| label: pp-impact-of-changes-ip-bed-days

ip_pcf |> 
  mod_principal_change_factor_effects_summarised("beddays", TRUE) |>
  mod_principal_change_factor_effects_cf_plot()
```

###### Admissions

```{r}
#| label: pp-impact-of-changes-ip-admissions

ip_pcf |> 
  mod_principal_change_factor_effects_summarised("admissions", TRUE) |>
  mod_principal_change_factor_effects_cf_plot()
```

##### Outpatients

###### Attendances

```{r}
#| label: pp-impact-of-changes-op-attendances

op_pcf |> 
  mod_principal_change_factor_effects_summarised("attendances", TRUE) |>
  mod_principal_change_factor_effects_cf_plot()
```

###### Tele-attendances

```{r}
#| label: pp-impact-of-changes-op-tele-attendances

op_pcf |> 
  mod_principal_change_factor_effects_summarised("tele_attendances", TRUE) |>
  mod_principal_change_factor_effects_cf_plot()
```

##### A&E

###### Arrivals

```{r}
#| label: pp-impact-of-changes-aae-arrivals

aae_pcf |> 
  mod_principal_change_factor_effects_summarised("arrivals", TRUE) |>
  mod_principal_change_factor_effects_cf_plot()
```

#### Summary by year

##### Values

```{r}
#| label: pp-summary-by-year

principal_high_level_summary_data <- 
  mod_principal_high_level_pods() |> 
  mod_principal_high_level_summary_data(r, pods = _, params$sites)

principal_high_level_summary_data |> 
  mod_principal_high_level_table(summary_type = "value")
```

##### Change

```{r}
#| label: pp-summary-by-year-change

principal_high_level_summary_data |> 
  mod_principal_high_level_table(summary_type = "change")
```

##### Percent change

```{r}
#| label: pp-summary-by-year-percent-change

principal_high_level_summary_data |> 
  mod_principal_high_level_table(summary_type = "change_pcnt")
```


##### Inpatient admissions

```{r}
#| label: pp-summary-by-year-plot-ip

principal_high_level_summary_data |> 
  mod_principal_high_level_plot(activity_type = "ip")
```

##### Outpatient attendances

```{r}
#| label: pp-summary-by-year-plot-op

principal_high_level_summary_data |> 
  mod_principal_high_level_plot(activity_type = "op")
```

##### A&E attendances

Available at trust level only.

```{r}
#| label: pp-summary-by-year-plot-aae

principal_high_level_summary_data |> 
  mod_principal_high_level_plot(activity_type = "aae")
```

#### Activity in detail

```{r}
#| label: pp-activity-in-detail-setup

tretspef_lookup <- jsonlite::read_json(
  app_sys("app", "data", "tx-lookup.json"),
  simplifyVector = TRUE
) |>
  dplyr::mutate(
    dplyr::across("Description", \(x) stringr::str_remove(x, " Service$")),
    dplyr::across("Description", \(x) paste0(.data$Code, ": ", .data$Description)),
  ) |>
  dplyr::select(-"Group")

# Function to prepare data and table

generate_activity_in_detail_table <- function(
    activity_type, pod, measure, agg_col
) {
  
  aggregated_data <- params$r |>
    get_aggregation(pod, measure, agg_col, NULL) |>
    shiny::req() |>
    dplyr::transmute(
      .data$sex,
      agg = .data[[agg_col]],
      .data$baseline,
      final = .data$principal,
      change = .data$final - .data$baseline,
      change_pcnt = .data$change / .data$baseline
    )
  
  if (agg_col == "tretspef") {
    aggregated_data <- aggregated_data |>
      dplyr::left_join(
        tretspef_lookup,
        by = dplyr::join_by("agg" == "Code")
      ) |>
      dplyr::mutate(
        dplyr::across(
          "Description",
          \(x) dplyr::if_else(is.na(x), .data$agg, .data$Description)
        ),
      ) |>
      dplyr::select("sex", "Description", dplyr::everything(), -"agg") |>
      dplyr::rename("agg" = "Description")
  }
  
  end_year <- params$r[["params"]][["end_year"]]
  end_fyear <- paste0(
    end_year, "/",
    as.numeric(stringr::str_extract(end_year, "\\d{2}$")) + 1
  )
  
  aggregated_data |> 
    mod_principal_detailed_table(
      aggregation = agg_col,
      final_year = end_fyear
    ) |> 
    gt::tab_options(table.width = gt::pct(100))
  
}

possibly_generate_activity_in_detail_table <- purrr::possibly(
  generate_activity_in_detail_table,
  otherwise = "Insufficient information to produce this table"
)

# Prepare sets of inputs (activity, pods, measure, aggregation, sites)

atpmo_agg <- get_activity_type_pod_measure_options() |> 
  dplyr::select("activity_type", "pod", "measure" = "measures") |> 
  tidyr::crossing(agg_col = c("age_group", "tretspef")) |> 
  dplyr::mutate(
    activity_type = dplyr::case_match(
      activity_type, 
      "ip" ~ "inpatients",
      "op" ~ "outpatients",
      "aae" ~ "aae"
    )
  )

activity_in_detail_table_names <- atpmo_agg |> 
  dplyr::mutate(table_name = paste(pod, measure, agg_col, sep = "_")) |>
  dplyr::pull()

# Prepare a list with each set of input combos

activity_in_detail_tables <- purrr::pmap(
  atpmo_agg, 
  possibly_generate_activity_in_detail_table
) |> 
  purrr::set_names(activity_in_detail_table_names)
```

##### Inpatients

###### Elective admissions

Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-1

activity_in_detail_tables$ip_elective_admission_admissions_age_group
```

Admissions by age group by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-2

activity_in_detail_tables$ip_elective_admission_admissions_tretspef
```

Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-3

activity_in_detail_tables$ip_elective_admission_beddays_age_group
```

Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-4

activity_in_detail_tables$ip_elective_admission_beddays_tretspef
```

###### Elective daycases

Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-5

activity_in_detail_tables$ip_elective_daycase_admissions_age_group
```

Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-6

activity_in_detail_tables$ip_elective_daycase_admissions_tretspef
```

Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-7

activity_in_detail_tables$ip_elective_daycase_beddays_age_group
```

Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-8

activity_in_detail_tables$ip_elective_daycase_beddays_tretspef
```

###### Maternity

Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-9

activity_in_detail_tables$ip_maternity_admission_admissions_age_group
```

Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-10

activity_in_detail_tables$ip_maternity_admission_admissions_tretspef
```

Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-11

activity_in_detail_tables$ip_maternity_admission_beddays_age_group
```

Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-12

activity_in_detail_tables$ip_maternity_admission_beddays_tretspef
```

###### Non-elective

Admissions by age group

```{r}
#| label: pp-activity-in-detail-ip-13

activity_in_detail_tables$`ip_non-elective_admission_admissions_age_group`
```

Admissions by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-14

activity_in_detail_tables$`ip_non-elective_admission_admissions_tretspef`
```

Bed days by age group

```{r}
#| label: pp-activity-in-detail-ip-15 

activity_in_detail_tables$`ip_non-elective_admission_beddays_age_group`
```

Bed days by treatment specialty

```{r}
#| label: pp-activity-in-detail-ip-16 

activity_in_detail_tables$`ip_non-elective_admission_beddays_tretspef`
```

##### Outpatients

###### First

Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-1

activity_in_detail_tables$op_first_attendances_age_group
```

Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-2

activity_in_detail_tables$op_first_attendances_tretspef
```

Tele-attendances by age group

```{r}
#| label: pp-activity-in-detail-op-3

activity_in_detail_tables$op_first_tele_attendances_age_group
```

Tele-attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-4

activity_in_detail_tables$op_first_tele_attendances_tretspef
```

###### Follow-up

Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-5

activity_in_detail_tables$`op_follow-up_attendances_age_group`
```

Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-6

activity_in_detail_tables$`op_follow-up_attendances_tretspef`
```

Tele-attendances by age group

```{r}
#| label: pp-activity-in-detail-op-7

activity_in_detail_tables$`op_follow-up_tele_attendances_age_group`
```

Tele-attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-8

activity_in_detail_tables$`op_follow-up_tele_attendances_tretspef`
```

###### Procedure

Attendances by age group

```{r}
#| label: pp-activity-in-detail-op-9

activity_in_detail_tables$op_procedure_attendances_age_group
```

Attendances by treatment specialty

```{r}
#| label: pp-activity-in-detail-op-10

activity_in_detail_tables$op_procedure_attendances_tretspef
```

##### A&E

###### Type 1 department

Ambulance by age group

```{r}
#| label: pp-activity-in-detail-aae-1

activity_in_detail_tables$`aae_type-01_ambulance_age_group`
```

Ambulance by treatment specialty

```{r}
#| label: pp-activity-in-detail-aae-2

activity_in_detail_tables$`aae_type-01_ambulance_tretspef`
```

Walk-in by age group

```{r}
#| label: pp-activity-in-detail-aae-3

activity_in_detail_tables$`aae_type-01_walk-in_age_group`
```

Walk-in by treatment specialty

```{r}
#| label: pp-activity-in-detail-aae-4

activity_in_detail_tables$`aae_type-01_walk-in_tretspef`
```

###### Type 2 department

Ambulance by age group

```{r}
#| label: pp-activity-in-detail-aae-5

activity_in_detail_tables$`aae_type-02_ambulance_age_group`
```

Ambulance by treatment specialty

```{r}
#| label: pp-activity-in-detail-aae-6

activity_in_detail_tables$`aae_type-02_ambulance_tretspef`
```

Walk-in by age group

```{r}
#| label: pp-activity-in-detail-aae-7

activity_in_detail_tables$`aae_type-02_walk-in_age_group`
```

Walk-in by treatment specialty

```{r}
#| label: pp-activity-in-detail-aae-8

activity_in_detail_tables$`aae_type-02_walk-in_tretspef`
```

###### Type 3 department

Ambulance by age group

```{r}
#| label: pp-activity-in-detail-aae-9

activity_in_detail_tables$`aae_type-03_ambulance_age_group`
```

Ambulance by treatment specialty

```{r}
#| label: pp-activity-in-detail-aae-10

activity_in_detail_tables$`aae_type-03_ambulance_tretspef`
```

Walk-in by age group

```{r}
#| label: pp-activity-in-detail-aae-11

activity_in_detail_tables$`aae_type-03_walk-in_age_group`
```

Walk-in by treatment specialty

```{r}
#| label: pp-activity-in-detail-aae-12

activity_in_detail_tables$`aae_type-03_walk-in_tretspef`
```

###### Type 4 department

Ambulance by age group

```{r}
#| label: pp-activity-in-detail-aae-13

activity_in_detail_tables$`aae_type-04_ambulance_age_group`
```

Ambulance by treatment specialty

```{r}
#| label: pp-activity-in-detail-aae-14

activity_in_detail_tables$`aae_type-04_ambulance_tretspef`
```

Walk-in by age group

```{r}
#| label: pp-activity-in-detail-aae-15

activity_in_detail_tables$`aae_type-04_walk-in_age_group`
```

Walk-in by treatment specialty

```{r}
#| label: pp-activity-in-detail-aae-16

activity_in_detail_tables$`aae_type-04_walk-in_tretspef`
```

### Distribution of projections

#### Activity summary

```{r}
#| label: dop-activity-summary

atpmo <- get_activity_type_pod_measure_options()

params$r |>
  get_model_core_activity(params$sites) |>
  dplyr::inner_join(atpmo, by = c("pod", "measure" = "measures")) |> 
  mod_model_core_activity_server_table() |> 
  gt::tab_options(table.width = gt::pct(100))
```

#### Activity distribution

```{r}
#| label: dop-activity-distribution-setup

# Prepare sets of inputs (activity, pods, measure, aggregation, sites)

atpmo_simplified <- get_activity_type_pod_measure_options() |> 
  dplyr::select("activity_type", "pod", "measure" = "measures") |> 
  dplyr::mutate(
    activity_type = dplyr::case_match(
      activity_type, "ip" ~ "inpatients", "op" ~ "outpatients", "aae" ~ "aae"
    )
  )

activity_distribution_table_names <- atpmo_simplified |> 
  dplyr::mutate(table_name = paste(pod, measure, sep = "_")) |>
  dplyr::pull()

# Functions to prepare data and plot 

generate_activity_distribution_beeswarm <- function(
    activity_type, pod, measure
) {
  
  selected_measure <- c(activity_type, pod, measure)
  
  aggregated_data <- params$r |>
    mod_model_results_distribution_get_data(selected_measure, params$sites) |>
    require_rows()
  
  mod_model_results_distribution_beeswarm_plot(
    aggregated_data,
    show_origin = FALSE
  )
  
}

generate_activity_distribution_ecdf <- function(activity_type, pod, measure) {
  
  selected_measure <- c(activity_type, pod, measure)
  
  aggregated_data <- params$r |>
    mod_model_results_distribution_get_data(selected_measure, params$sites) |>
    require_rows()
  
  mod_model_results_distribution_ecdf_plot(
    aggregated_data,
    show_origin = FALSE
  )
  
}

possibly_generate_activity_distribution_beeswarm <- purrr::possibly(
  generate_activity_distribution_beeswarm,
  otherwise = "Insufficient information to produce this chart"
)

possibly_generate_activity_distribution_ecdf <- purrr::possibly(
  generate_activity_distribution_ecdf,
  otherwise = "Insufficient information to produce this chart"
)

# Prepare a list with each set of input combos

activity_distribution_beeswarms <- atpmo_simplified |> 
  purrr::pmap(possibly_generate_activity_distribution_beeswarm) |> 
  purrr::set_names(activity_distribution_table_names)

activity_distribution_ecdfs <- atpmo_simplified |> 
  purrr::pmap(possibly_generate_activity_distribution_ecdf) |> 
  purrr::set_names(activity_distribution_table_names)
```

##### Inpatients

###### Non-elective admission

Admissions

```{r}
#| label: pp-activity-distribution-ip-1

activity_distribution_beeswarms$`ip_non-elective_admission_admissions`
activity_distribution_ecdfs$`ip_non-elective_admission_admissions`
```

Bed days

```{r}
#| label: pp-activity-distribution-ip-2

activity_distribution_beeswarms$`ip_non-elective_admission_beddays`
activity_distribution_ecdfs$`ip_non-elective_admission_beddays`
```

###### Elective admission

```{r}
#| label: pp-activity-distribution-ip-3

activity_distribution_beeswarms$`ip_elective_admission_admissions`
activity_distribution_ecdfs$`ip_elective_admission_admissions`
```

Bed days

```{r}
#| label: pp-activity-distribution-ip-4

activity_distribution_beeswarms$`ip_elective_admission_beddays`
activity_distribution_ecdfs$`ip_elective_admission_beddays`
```

###### Maternity admission

```{r}
#| label: pp-activity-distribution-ip-5

activity_distribution_beeswarms$`ip_maternity_admission_admissions`
activity_distribution_ecdfs$`ip_maternity_admission_admissions`
```

Bed days

```{r}
#| label: pp-activity-distribution-ip-6

activity_distribution_beeswarms$`ip_maternity_admission_beddays`
activity_distribution_ecdfs$`ip_maternity_admission_beddays`
```

##### Outpatients

###### First

Attendances

```{r}
#| label: pp-activity-distribution-ip-7

activity_distribution_beeswarms$`op_first_attendances`
activity_distribution_ecdfs$`op_first_attendances`
```

Tele-attendances

```{r}
#| label: pp-activity-distribution-ip-8

activity_distribution_beeswarms$`op_first_tele_attendances`
activity_distribution_ecdfs$`op_first_tele_attendances`
```

###### Follow-up

Attendances

```{r}
#| label: pp-activity-distribution-ip-9

activity_distribution_beeswarms$`op_follow-up_attendances`
activity_distribution_ecdfs$`op_follow-up_attendances`
```

Tele-attendances

```{r}
#| label: pp-activity-distribution-ip-10

activity_distribution_beeswarms$`op_follow-up_tele_attendances`
activity_distribution_ecdfs$`op_follow-up_tele_attendances`
```

##### A&E

###### Type 1

Ambulance

```{r}
#| label: pp-activity-distribution-ip-11

activity_distribution_beeswarms$`aae_type-01_ambulance`
activity_distribution_ecdfs$`aae_type-01_ambulance`
```

Walk-in

```{r}
#| label: pp-activity-distribution-ip-12

activity_distribution_beeswarms$`aae_type-01_walk-in`
activity_distribution_ecdfs$`aae_type-01_walk-in`
```

###### Type 2

Ambulance

```{r}
#| label: pp-activity-distribution-ip-13

activity_distribution_beeswarms$`aae_type-02_ambulance`
activity_distribution_ecdfs$`aae_type-02_ambulance`
```

Walk-in

```{r}
#| label: pp-activity-distribution-ip-14

activity_distribution_beeswarms$`aae_type-02_walk-in`
activity_distribution_ecdfs$`aae_type-02_walk-in`
```

###### Type 3

Ambulance

```{r}
#| label: pp-activity-distribution-ip-15

activity_distribution_beeswarms$`aae_type-03_ambulance`
activity_distribution_ecdfs$`aae_type-03_ambulance`
```

Walk-in

```{r}
#| label: pp-activity-distribution-ip-16

activity_distribution_beeswarms$`aae_type-03_walk-in`
activity_distribution_ecdfs$`aae_type-03_walk-in`
```

###### Type 4

Ambulance

```{r}
#| label: pp-activity-distribution-ip-17

activity_distribution_beeswarms$`aae_type-04_ambulance`
activity_distribution_ecdfs$`aae_type-04_ambulance`
```

Walk-in

```{r}
#| label: pp-activity-distribution-ip-18

activity_distribution_beeswarms$`aae_type-04_walk-in`
activity_distribution_ecdfs$`aae_type-04_walk-in`
```

